Characteristic polynomials of p-adic matrices

### 2017-04-17 charpoly/charpoly.tex
Addressed some more reviewer suggestions

\item \tdo{What are the implications, if any, of your work on well-known methods such as Dixon's algorithm?}
\item \tdo{In section 3, Algorithm 1: what is the cost of step 5, and how did you avoid quartic complexity?}\\
      \xavier{I think that the cost is $O(n^2)$ because it corresponds to an elementary operation of rows/columns. Is that correct?} \\
      \david{I agree.  I think we just need to explain that the matrix products are just notational, not actually computed.}
\item \tdo{In section 4, give a concrete construction for approximating the characteristic polynomial as a ``by product'' of the work of [15].}\\
      \xavier{I do not really understand this remark. I mean: once we have the Frobenius invariants, the characteristic polynomial is just the product of them, isn't it?}\\
      \david{Agreed.  I think I can clarify the language somewhat, but there's no real work to be done.}

@@

with the fact that we do degree one approx of a charpoly)}

@@

\item \tdo{In the experiments, (section 5.1), it is not clear which of the two methods is being used to compute the comatrix.}\\
      \xavier{Ok but it is not important (since we are just interested in the result). Should we really say more about that? (In practice, I think that we used the \texttt{adjoint} method of \textsc{sage}.)}\\
      \david{I had the same reaction when I first saw the results.  I think we can say something to make clearer that it doesn't matter how it is computed.}

@@

@@

From now on, we fix a matrix $M \in M_n(K)$ for which $d \chi_M$ is 
surjective. Let $(\alpha, P, Q, \chi_M)$ be the quadruple encoding
the short form of $d \chi_M$; we recall that they are related by the
relations:
\begin{align*}
d \chi_M(dM) & =\tr(\adj(X{-}M) \cdot dM) \\
\adj(X{-}M) & = \alpha \cdot P Y^T \cdot Y Q^T \mod \chi_M.
\end{align*}
An approximation to $\chi_M$ can be computed in $\softO(n^\omega)$ operations in $K$
(\textit{e.g.} as a by-product of \cite{storjohann:01a}).

@@

\begin{enumerate}[$\bullet$]
\renewcommand{\itemsep}{0pt}
\item the optimal precision on the $k$-th coefficient of the 
characteristic polynomial of $M$ given by Eq.~\eqref{eq:optjagged}
\item in the capped relative model\footnote{Each 
coefficient carries its own precision which is updated after each 
elementary arithmetical operation.},
the precision gotten on the $k$-th coefficient of the 
characteristic polynomial of $M$ computed \emph{via} the call:

\hfill$M\texttt{.charpoly(algorithm="df")}$\hfill\null

>>>>

\item \tdo{What are the implications, if any, of your work on well-known methods such as Dixon's algorithm?}\\
     \david{Do either of you know what Dixon's algorithm refers to in this context?}
\item \done{In section 3, Algorithm 1, we have clarified why line 5 does not take quartic time} \\
      \david{Tristan, can you check that my clarification before Proposition 3.2 is correct?}
\item \done{In section 4, we clarified how the characteristic polynomial is a by-product of [15].}

@@

with the fact that we do degree one approx of a charpoly)}\\

@@

\item \done{In section 5.1, we added a remark noting that the method for computing the adjugate matrix has no effect on the extent of the precision loss, just on the runtime.}

@@

Note that we use the notation of matrix multiplication in line 5, but actual updating of
$H$ and $P$ uses row and column operations.

@@

From now on, we fix a matrix $M \in M_n(K)$ for which $d \chi_M$ is 
surjective. Let $(\alpha, P, Q, \chi_M)$ be the quadruple encoding
the short form of $d \chi_M$; we recall that they are related by the
relations:
\begin{align*}
d \chi_M(dM) & =\tr(\adj(X{-}M) \cdot dM) \\
\adj(X{-}M) & = \alpha \cdot P Y^T \cdot Y Q^T \mod \chi_M.
\end{align*}
An approximation to $\chi_M$ can be computed in $\softO(n^\omega)$ operations in $K$
by computing an approximation to the Frobenius normal form of $M$ \cite{storjohann:01a}.

@@

\begin{enumerate}[$\bullet$]
\renewcommand{\itemsep}{0pt}
\item the optimal precision on the $k$-th coefficient of the 
characteristic polynomial of $M$ given by Eq.~\eqref{eq:optjagged}.
Note that it does not matter which method we use to compute $\adj(X-M)$,
since we are only interested in the precision loss and not the runtime.
\item in the capped relative model\footnote{Each 
coefficient carries its own precision which is updated after each 
elementary arithmetical operation.},
the precision gotten on the $k$-th coefficient of the 
characteristic polynomial of $M$ computed \emph{via} the call:

\hfill$M\texttt{.charpoly(algorithm="df")}.$\hfill\null
